Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-09-01 manuscript_thev_transcriptome.Rmd
Fixed table sizes in pdf

set_flextable_defaults(font.size = 8)
t1 <- flextable(tab1) %>% theme_zebra() %>%
  set_table_properties(layout = "fixed", width = 0.95,
                       opts_pdf = list(caption_repeat = F)) %>%
  font(part = "all", fontname = "Avenir") %>%
  width(., j = "Metric", 1.5) %>%
  set_caption("Overview of sequencing results",
              style = "Table Caption")
bold(t1, j = "Metric", bold = T)

@@

```{r}
#| tab.id: NULL
#| tab.cap.pre: ""
#| tab.cap.sep: ""
set_flextable_defaults(font.size = 8)
flextable(sig_12_juncs) %>% theme_zebra() %>%
  set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  font(part = "all", fontname = "Avenir") %>%
  set_caption("Table 2a: Most abundant splice junctions at 12h.p.i",
              style = "Table Caption")
```
\newpage

```{r}
#| tab.id: NULL
set_flextable_defaults(font.size = 8)
flextable(sig_24_juncs) %>% theme_zebra() %>%
  set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  font(part = "all", fontname = "Avenir") %>%
  set_caption("Table 2b: Most abundant splice junctions at 24h.p.i",
              style = "Table Caption")
```
\newpage

```{r}
#| tab.id: NULL
set_flextable_defaults(font.size = 8)
flextable(sig_72_juncs) %>% theme_zebra() %>%
  set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  font(part = "all", fontname = "Avenir") %>%
  set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
              style = "Table Caption")
```
\newpage

>>>>

set_flextable_defaults(font.size = 8)
flextable(tab1) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 0.95,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::width(., j = ~ Metric, width = 1.5) %>%
  flextable::set_caption("Overview of sequencing results",
              style = "Table Caption") %>%
  flextable::bold(part = "body", j = ~ Metric)

@@

```{r}
#| tab.id: NULL
#| tab.cap.pre: ""
#| tab.cap.sep: ""
set_flextable_defaults(font.size = 8)
flextable(sig_12_juncs) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_caption("Table 2a: Most abundant splice junctions at 12h.p.i",
              style = "Table Caption") %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.7) %>%
  flextable::width(., j = ~ Reads_Percentage, width = 1)
```
\newpage

```{r}
#| tab.id: NULL
set_flextable_defaults(font.size = 8)
flextable(sig_24_juncs) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_caption("Table 2b: Most abundant splice junctions at 24h.p.i",
              style = "Table Caption") %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.7) %>%
  flextable::width(., j = ~ Reads_Percentage, width = 1)
```
\newpage

```{r}
#| tab.id: NULL
set_flextable_defaults(font.size = 8)
flextable(sig_72_juncs) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
              style = "Table Caption") %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.7) %>%
  flextable::width(., j = ~ Reads_Percentage, width = 1)
```
\newpage
